---
title: "R Notebook"
output: html_notebook
---

Week 2 Day 2 Homework 

Q1.1

```{r}
library(RPostgreSQL)

```

```{r}


library(keyring)

keyring_unlock("local")

username <- key_get(service = "postgresql_username", keyring = "local")

password <- key_get(service = "postgresql_password", keyring = "local")

keyring_lock("local")


```

```{r}
db_connection <- dbConnect(drv = PostgreSQL(max.con = 2), 
                              user = username,
                              password = password, 
                              dbname = "wrestling", 
                              host = "localhost")

rm(username)
rm(password)
```

```{r}
dbGetQuery(db_connection, 
           "SELECT * FROM wrestlers")


#id - INT/primary key 
#born - VARCHAR
#name - VARCHAR
#gender - VARCHAR
#win_percent - REAL/INT
#total_matches - INT
```



```{r}
dbDisconnect(conn = db_connection)
```

1.2 Remote PostgreSQL Connections 

I did the first parts of this in the R Console 

```{r}
# username: 'mvhbdgdk'
# password: 'Ejn5vEqOUfCA1Cxg1rqkh9NY5VbKKAIm'
# database_name: 'mvhbdgdk'
# host: 'manny.db.elephantsql.com' or '34.245.37.126' (these are equivalent)
```

```{r}
keyring_unlock("remote")

username <- key_get(service = "wrestling_postgresql_username", keyring = "remote")
password <- key_get(service = "wrestling_postgresql_password", keyring = "remote")

keyring_lock("remote")


rm(username)
rm(password)
```


```{r}

remote_db_connection <- dbConnect(drv = PostgreSQL(max.con = 2), 
                              user = username,
                              password = password, 
                              dbname = "mvhbdgdk", 
                              host = "manny.db.elephantsql.com")


dbGetQuery(remote_db_connection, 
           "SELECT * FROM wrestlers")
```


```{r}
dbDisconnect(remote_db_connection)

```


Extension 
1 Return all the details for any wrestlers from the United Kingdom
```{r}
username <- key_get(service = "postgresql_username", keyring = "local")

password <- key_get(service = "postgresql_password", keyring = "local")

keyring_lock("local")

db_connection <- dbConnect(drv = PostgreSQL(max.con = 2), 
                              user = username,
                              password = password, 
                              dbname = "wrestling", 
                              host = "localhost")

rm(username)
rm(password)


dbGetQuery(db_connection, 
           "SELECT * FROM wrestlers
           WHERE born = 'United Kingdom'")
```

2 Get the names of all Japanese wrestlers who have appeared in 40 or more matches.
```{r}
dbGetQuery(db_connection, 
           "SELECT * FROM wrestlers
           WHERE born = 'Japan'
           AND total_matches >= 40")
```

3Find the wrestlers who have won between 50% and 60% of their matches
```{r}
dbGetQuery(db_connection, 
           "SELECT * FROM wrestlers
            WHERE win_percent BETWEEN 50 AND 60")
```


4 Find all the wrestlers with names beginning with ‘X’
```{r}
dbGetQuery(db_connection, 
           "SELECT * FROM wrestlers
            WHERE name LIKE 'X%'")
```

5 Find all the wrestlers who were born in countries beginning with the letter ‘I’. Try this using IN (there are 9 countries) and using a wildcard comparison.
```{r}
dbGetQuery(db_connection, 
           "SELECT * FROM wrestlers
            WHERE born LIKE 'I%'")

dbGetQuery(db_connection, 
           "SELECT COUNT(*) FROM wrestlers
            WHERE born LIKE 'I%'")

```



6 Find all the wrestlers who were not born in countries beginning with the letter ‘I
```{r}
dbGetQuery(db_connection, 
           "SELECT * FROM wrestlers
            WHERE NOT born LIKE 'I%'")
```

```{r}
dbDisconnect(db_connection)
```

