---
title: "R Notebook"
output: html_notebook
---
#Homework: Week 11 Day 1 



```{r}
library(tidyverse)
library(janitor)
library(infer)

data(msleep)

msleep
```


```{r}
head(msleep)

glimpse(msleep)
```

Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.


alpha = 0.05

H0: sleep_total = 7
HA: sleep_total != 7 
```{r}

observed_stat <- msleep %>% 
  summarise(mean_total_sleep = mean(sleep_total))


null_distribution <- msleep %>%
  specify(response = sleep_total) %>%
  hypothesize(null = "point", mu = 7) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")

null_distribution %>% 
  visualise(bins = 30) + 
  shade_p_value(obs_stat = observed_stat, direction = "both")
  

null_distribution %>% 
  get_p_value(obs_stat = observed_stat, direction = "both")

#p_value less than 0.05 so we have sufficient evidence to reject the null that average sleep for our sample is different to that of the jabberwocky 


```


Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

What type of test? 

 - indepent samples I think...
 
alpha = 0.05

H0: mean_sleep(omnivore) - mean_sleep(herbivore) = 0
HA: mean_sleep(omnivore) - mean_sleep(hervibore) > 0


```{r}

omni_herbi <- msleep %>% 
  filter(vore == "herbi" | vore == "omni")

omni_herbi %>% 
  group_by(vore) %>%
  summarise(n = n())


omni_herbi %>% 
  group_by(vore) %>% 
  ggplot(aes(x = vore, y = sleep_total)) + 
  geom_boxplot()


```


```{r}
null_dist_vore <- omni_herbi %>% 
  specify(sleep_total ~ vore) %>% 
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))

#now need observed stat

obs_stat_vore <- omni_herbi %>% 
  specify(sleep_total ~ vore) %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))


null_dist_vore %>% 
  visualise(bins = 30) + 
  shade_p_value(obs_stat = obs_stat_vore, direction = "right")

null_dist_vore %>%
  get_p_value(obs_stat = obs_stat_vore, direction = "right")
  

#p-value 0.121 means we fail to reject the null hypo that difference in mean sleep across omnis and herbis is zero 


```


Perform an appropriate statistical test to determine whether the proportion of domesticated animals in the population of animal types is greater than 5%.

```{r}
obs_dom_stat <- msleep %>% 
  filter(conservation == "domesticated") %>%
  summarise(prop_dom = n() / nrow(msleep))

msleep %>% 
  group_by(conservation) %>% 
  summarise(n())
  
```
alpha = 0.05

H0: prop_dom = 0.05

HA: prop_dom > 0.05

```{r}
#create domesticated flag 

msleep_dom <- msleep %>% 
  mutate(domestic_flag = ifelse(conservation == "domesticated", 
                                "dom", "not_dom")) %>% 
  filter(!is.na(domestic_flag))


```


```{r}
null_distribution_dom <- msleep_dom %>%
  specify(response = domestic_flag, success = "dom") %>% 
  hypothesize(null = "point", p = 0.05) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "prop") 


null_distribution_dom %>% 
  visualise(bins = 30) + 
  shade_p_value(obs_stat = obs_dom_stat, direction = "right")

null_distribution_dom %>% 
  get_p_value(obs_stat = obs_dom_stat, direction = "right")

#reject HO in favour of HA 
```


