---
title: "R Notebook"
output: html_notebook
---

# Text Analysis Homework

```{r}
library(tidyverse)
library(tidytext)
library(janeaustenr)
```

1.Find the most common words in both Pride & Prejudice and Sense & Sensibility.
```{r}

p_and_p <- tibble(
  text = prideprejudice, 
  line_id = (1:length(prideprejudice))
)

p_and_p <- p_and_p %>%
  unnest_tokens(word, text) 

p_and_p %>%
  count(word, sort = TRUE)
  

s_and_s <- tibble(
  text = sensesensibility, 
  line_id = (1:length(sensesensibility))
) 

s_and_s <- s_and_s %>%
  unnest_tokens(word, text) 

s_and_s %>%
  count(word, sort = TRUE)

```



2. Find the most common words in both Pride & Prejudice and Sense & Sensibility, not including stop words.

```{r}
p_and_p %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
```

```{r}
s_and_s %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
```


3. Find the most common sentiment words in both Pride & Prejudice and Sense & Sensibility.

```{r}

# for negative P and P 

p_and_p_negative <- p_and_p %>%
  inner_join(get_sentiments("loughran")) %>%
  filter(sentiment == "negative") %>%
  count(word, sort = TRUE)

#for negative S and S 


s_and_s_negative <- s_and_s %>%
  inner_join(get_sentiments("loughran")) %>%
  filter(sentiment == "negative") %>%
  count(word, sort = TRUE)


p_and_p_negative %>%
  inner_join(s_and_s_negative) 

```



```{r}
# for positive loughran sentiment analysis 

#p and p 

p_and_p %>%
  inner_join(get_sentiments("loughran")) %>%
  filter(sentiment == "positive") %>%
  count(word, sort = TRUE)


s_and_s %>%
  inner_join(get_sentiments("loughran")) %>%
  filter(sentiment == "positive") %>%
  count(word, sort = TRUE)

# it seems that sentiment wise, both novels are v similar 


```


Now want to get these sentiments as scores to be able to plot them 

Will use the afinn sentiments data 

```{r}
p_and_p_numeric <- p_and_p %>%
  inner_join(get_sentiments("afinn"))

s_and_s_numeric <- s_and_s %>%
  inner_join(get_sentiments("afinn"))
```




Extension 

Taking your results above. Can you create a plot which visualises the differences between the books?

```{r}
p_and_p_numeric %>%
  summarise(max(line_id))

library(viridis)
```






```{r}

```

```{r}

p_and_p_2 <- p_and_p_numeric %>%
  group_by(line_id) %>%
  mutate(mean_sent = mean(value))

p_and_p_2 %>%
   ggplot(aes(x = line_id, y = mean_sent)) + 
  geom_bar(stat = "identity", fill = "indianred") + 
  theme_minimal() + 
  labs(title = "Pride and Prejudice: sentiment analysis")



s_and_s_numeric %>%
  group_by(line_id) %>%
  mutate(mean_sent = mean(value)) %>%
   ggplot(aes(x = line_id, y = mean_sent)) + 
  geom_bar(stat = "identity", fill = "purple") + 
  theme_minimal() + 
  labs(title = "Sense and Sensibility: sentiment analysis")
```



```{r}
s_and_s_numeric %>%
  group_by(line_id) %>%
  mutate(mean_sent = mean(value)) %>%
   ggplot(aes(x = line_id, y = mean_sent)) + 
  geom_area(alpha = 0.7)+ 
  theme_minimal() + 
  labs(title = "Sense and Sensibility: sentiment analysis")
```











