---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

# Advanced ggplot homework

```{r}
library(tidyverse)
library(CodeClanData)
library(ggthemes)
library(extrafont)

fonts()

col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")

company_theme <- theme_bw(base_size = 12, base_family = "Trebuchet MS") +
  theme(
        panel.border     = element_blank(), 
        panel.background = element_rect(fill   = "white",  colour = "white"),
        panel.grid.major = element_line(colour = "grey95", size   = 0.5), 
        panel.grid.minor = element_line(colour = "grey95", size   = 0.5)
)
```

1. Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

```{r}
qb_revenue_breakdown

ggplot(qb_revenue_breakdown) + 
  aes(x = Year, y = Revenue, fill = Product) + 
  geom_col(position = "stack") + 
  scale_fill_manual(values = col_scheme) +
  company_theme + 
  labs(
    title = "Revenue in 2018 and 2019 by Product"
  )

```

2. Make a line chart showing monthly sales of the “flagship product” - the KwikBit Unit1 - over the last year. This data is inside qb_monthly_sales, but you will need to use subset.

```{r}

view(qb_monthly_sales)

qb_monthly_sales %>%
  filter(Cashflow == "Kwikbit Unit 1 Sales") %>%
  ggplot() + 
  aes(x = Date, y = Amount) + 
  geom_line(colour = "#E89FE9", size = 1) +
  labs(
    y     = "Sales of KwikBit Unit1", 
    title = "Sales of Flagship Product in the last year"
  ) + 
  company_theme

```

3. Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

```{r}
qb_monthly_sales %>%
  filter(Cashflow != "Kwikbit Unit 1 Sales") %>%
  mutate(rev_cost = if_else(Cashflow == "Total Revenue", "Total Revenue", "Cost")) %>%
  ggplot() +
  aes(x = Date, y = Amount, group = rev_cost, colour = Cashflow) + 
  geom_line(size = 1)  + 
  company_theme + 
  scale_colour_manual(values = col_scheme) + 
  labs(
    title = "Revenue and Costs 2018 - 2019"
  )

```

4. Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.
```{r}
view(qb_competitors)

qb_competitors %>%
  filter(Year == "2019") %>%
  summarise(sum(Revenue))

ggplot(qb_competitors) + 
  aes(x = Year, y = Revenue, fill = Company) + 
  geom_area() + 
  company_theme + 
  scale_fill_manual(values = col_scheme) + 
  scale_y_continuous(labels = scales::dollar_format(prefix = "£"))

ggplot(qb_competitors) + 
  aes(x = Year, y = Revenue, fill = Company) + 
  geom_area(position = "identity", alpha = 0.5) + 
  company_theme + 
  scale_fill_manual(values = col_scheme) + 
  scale_y_continuous(labels = scales::dollar_format(prefix = "£"))


```

5. Now show the sales from the 5 competitors as a line graph. Include an extra layer that shows the data points used to make the lines.

```{r}
ggplot(qb_competitors) + 
  aes(x = Year, y = Revenue, group = Company, colour = Company) +
  geom_line(size = 1.25) + 
  geom_point() + 
  company_theme + 
  scale_colour_manual(values = col_scheme) + 
  scale_y_continuous(labels = scales::dollar_format(prefix = "£"))
```

6. Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between individuals and devices. Data is in qb_device_data.

```{r}
view(qb_device_data)

tail(qb_device_data)
class(qb_device_data)

qb_device_data %>%
mutate( decimal_hour = (hours + mins)/60) %>%
ggplot() + 
  aes(x = decimal_hour, y = counts, colour = device) +  
  geom_line() + 
  facet_grid(id ~ device, scales = "free_y") +
  theme_bw(base_size = 12, base_family = "Trebuchet MS") +
  theme( 
        strip.background = element_blank(), 
        panel.border     = element_blank(), 
        panel.background = element_rect(fill   = "white",  colour = "white"),
        panel.grid.major = element_line(colour = "grey95", size   = 0.5), 
        panel.grid.minor = element_line(colour = "grey95", size   = 0.5)
) +
  scale_colour_manual(values = col_scheme) + 
  labs(
    title    = "KwikBit1 versus Competitor Products", 
    subtitle = "Activity of 5 Individuals over 24 Hours", 
    x = "Hour", 
    y = "Step Count", 
    caption = "Scales have been adjusted to improve interpretation"
  ) 
  
```

```{r}
qb_device_data_time <- qb_device_data %>%
  group_by(device, id) %>%
  mutate(total_hours  = hours + (mins/60),
         total_counts = cumsum(counts))
ggplot(qb_device_data_time, aes(x      = total_hours, 
                                y      = total_counts,
                                colour = device
                                )) +
   geom_line() +
   labs(
     y     = "Steps Counted",
     title = "Steps Counted By Device"
   ) +
   facet_wrap(~ id, ncol = 2) +
   company_theme +
   scale_colour_manual(values = col_scheme)
```

