---
title: "R Notebook"
output: html_notebook
---

# King Country Model Development Hw


I've been given a set of data on housing sale prices for the last few years in King County (near Seattle) between May 2014 and May 2015. Have a look at the variable definitions on the Kaggle page


First, tidy the data for regression 
```{r}

library(tidyverse)
kc_house_data <- read_csv("kc_house_data.csv")
```

You might like to think about removing some or all of date, id, sqft_living15, sqft_lot15 and zipcode (lat and long provide a better measure of location in any event).
```{r}
head(kc_house_data)


kc_house_tidy <- kc_house_data %>%
  select(-date, -id, -sqft_living15, -sqft_lot15, -zipcode)


```


Have a think about how to treat waterfront. Should we convert its type?
````{r}

class(kc_house_tidy$waterfront)

#waterfront appears to be a binary variable - we need to know what 1 and 0 stand for: 1 is overlooking waterfront, 0 not

#I'm not sure if there is a need to convert its type? 

```



We converted yr_renovated into a renovated logical variable, indicating whether the property had ever been renovated. You may wish to do the same.

```{r}
kc_house_tidy$yr_renovated

kc_house_tidy <- kc_house_tidy %>%
  mutate(renovated = ifelse(yr_renovated > 0, TRUE, FALSE)) %>% 
  select(-yr_renovated)

```


Have a think about how to treat condition and grade? Are they interval or categorical ordinal data types?
```{r}
kc_house_tidy %>% 
  distinct(condition)

kc_house_tidy %>%
  distinct(grade)

#because these are categories it makes sense to turn them into dummies 

library(fastDummies)

kc_dummies <- kc_house_tidy %>% 
  dummy_cols(select_columns = c("condition", "grade"), 
             remove_first_dummy = TRUE, 
             remove_selected_columns = TRUE)
```


```{r}
alias(price ~., kc_dummies)
```

Systematically build a regression model containing up to four main effects (remember, a main effect is just a single predictor with coefficient), testing the regression diagnostics as you go: 

(i) splitting datasets into numeric and non-numeric columns might help ggpairs() run in manageable time, although you will need to add either a price or resid column to the non-numeric dataframe in order to see its correlations with the non-numeric predictors.

```{r}
kc_num <- kc_house_tidy %>% 
  select(-renovated, -grade, -condition)

library(ggiraphExtra)

library(GGally)
ggpairs(kc_num)

```
Sorry R kept crashing so this is as far as I got...

```{r}

```

