---
title: "R Notebook"
output: html_notebook
---

# Analysing Telecomm Churn: Logistic Regression Lab 

```{r}
library(tidyverse)
library(readxl)
```

```{r}
telecomms_churn <- read_xlsx("telecomms_churn.xlsx")
```

```{r}

library(janitor)
telecomms_churn <- clean_names(telecomms_churn)


glimpse(telecomms_churn)
```

```{r}
head(telecomms_churn)


```

```{r}


#there are a lot of categorical variables in the data - in particular, churn is a categorical, meaning a logistic regression model is an appropriate classifier 
library(GGally)

telecomms_churn %>%
  select(-customer_id, -gender, - senior_citizen, -partner, -dependents, - phone_service, - internet_service, - contract) %>%
  ggpairs()

```


```{r}

telecomms_churn %>%
  ggplot(aes(x = senior_citizen, y = churn)) + 
  geom_bar(stat = "identity")

telecomms_churn %>%
  ggplot(aes(x = churn, y = )) + 
  geom_col(stat = "identity")

```
```{r}
telecomms_churn %>%
  distinct(contract)
```

```{r}

telecomms_churn %>% 
  select(-tenure, - monthly_charges, - total_charges, - customer_id, -gender, -senior_citizen, -partner, dependents) %>%
  ggpairs()

```





ggpairs v hard to interpret here 

```{r}

#I need to convert my columns that are characters to factors 

telecomms_churn_clean <- telecomms_churn %>%
  mutate_if(is.character, as_factor) %>%
  mutate(senior_citizen = if_else(
    senior_citizen == 1, "Yes", "No")
    ) %>%
  mutate(senior_citizen = as_factor(senior_citizen))


telecomms_churn_clean <- telecomms_churn_clean %>% 
  select(-customer_id)

```

```{r}

model_1 <- glm(churn ~ tenure, data = telecomms_churn_clean, 
               family = binomial(link = "logit"))

summary(model_1)

```


```{r}
model_2 <- glm(churn ~ monthly_charges, 
               data = telecomms_churn_clean, 
               family = binomial(link = "logit"))

summary(model_2)
```


```{r}
telecomms_churn_clean %>%
  distinct(contract)

model_3 <- glm(churn ~ contract, 
               data = telecomms_churn_clean, 
               family = binomial(link = "logit"))

summary(model_3)
```



Now I have three models and therefor three potential classifiers!

I want to compare each of these, so I'm going to plot their ROC curves and compare their AUC values 


```{r}
library(pROC)

library(modelr)

telecomms_churn_with_mod1_preds <- telecomms_churn_clean %>%
  add_predictions(model_1, type = "response")

roc_obj_model_1 <- telecomms_churn_with_mod1_preds %>%
  roc(response = churn, 
      predictor = pred)
```

```{r}
telecomms_churn_with_mod2_preds <- telecomms_churn_clean %>%
  add_predictions(model_2, type = "response")

roc_obj_model_2 <- telecomms_churn_with_mod2_preds %>%
  roc(response = churn, 
      predictor = pred)

```

```{r}
telecomms_churn_with_mod3_preds <- telecomms_churn_clean %>%
  add_predictions(model_3, type = "response")

roc_obj_model_3 <- telecomms_churn_with_mod3_preds %>%
  roc(response = churn, 
      predictor = pred)
```

Now I want to plot these roc curves to compare them 

```{r}
roc_comparison <- ggroc(list(
  "tenure model" = roc_obj_model_1,
  "monthly charges model" = roc_obj_model_2, 
  "contract type model" = roc_obj_model_3), 
                        legacy.axes = TRUE) + 
  coord_fixed() + 
  theme_minimal()

roc_comparison
```

Now want to compare the AUC of each model 
```{r}
tibble(
  auc = c(auc(roc_obj_model_1), auc(roc_obj_model_2), auc(roc_obj_model_3)),
  model = c("tenure", "monthly charges", "contract type")
)

```



Now for some cross-validation 

```{r}
library(caret)
```



```{r}
train_control <- trainControl(
  method = "repeatedcv", 
  number = 5, 
  repeats = 100, 
  savePredictions = TRUE, 
  classProbs = TRUE, 
  summaryFunction = twoClassSummary
)

model_1_cv <- train(churn ~ tenure, 
               data = telecomms_churn_clean, 
               trControl = train_control,
               method = "glm", 
               family = binomial(link = "logit")
)

```
```{r}
summary(model_1_cv)

model_1_cv$results
```

```{r}
train_control <- trainControl(
  method = "repeatedcv", 
  number = 5, 
  repeats = 100, 
  savePredictions = TRUE, 
  classProbs = TRUE, 
  summaryFunction = twoClassSummary
)

model_2_cv <- train(churn ~ monthly_charges, 
               data = telecomms_churn_clean, 
               trControl = train_control,
               method = "glm", 
               family = binomial(link = "logit")
)

model_2_cv$results

```

```{r}


model_3_cv <- train(churn ~ contract, 
               data = telecomms_churn_clean, 
               trControl = train_control,
               method = "glm", 
               family = binomial(link = "logit")
)

model_3_cv$results

```


So model 1 has the highest AUC 
```{r}
summary(model_1)


# interpreting the coefficent value 

#currently it is expressed in terms of log odds, so a unit 

telecomms_churn_clean %>%
  ggplot(aes(x = tenure)) + 
  geom_histogram()

odds_at_tenure_40 <- telecomms_churn_with_mod1_preds %>%
  filter(tenure == 40) %>%
  mutate(odds = pred/(1-pred)) %>%
  select(odds) %>%
  slice(1) 
  
```

```{r}

#how do the odds change if we decrease tenure by 20?
library(broom)

b_tenure_coeff <- tidy(model_1) %>%
  filter(term == "tenure") %>%
  select(estimate)


odds_factor <- exp(b_tenure_coeff * -20)

odds_at_tenure_20 <- odds_factor * odds_at_tenure_40

odds_at_tenure_20 - odds_at_tenure_40

# so a change in -20 of the tenure has led to an increase in the odds of churn of 0.255


```





```{r}
model_with_all <- glm(churn ~ ., 
                      data = telecomms_churn_clean, 
                      family = binomial(link = "logit"))

summary(model_with_all)
```




```{r}
train_control <- trainControl(
  method = "repeatedcv", 
  number = 5, 
  repeats = 100, 
  savePredictions = TRUE, 
  classProbs = TRUE, 
  summaryFunction = twoClassSummary
)

model_with_all_cv <- train(churn ~ ., 
               data = telecomms_churn_clean, 
               trControl = train_control,
               method = "glm", 
               family = binomial(link = "logit"), na.action = na.omit
)


model_with_all_cv$results

```

Think I'll remove partner and gender and try again

```{r}
model_multiple <- glm(churn ~
                        total_charges + monthly_charges + contract +
                        internet_service + phone_service + tenure + 
                        dependents + senior_citizen, 
                      data = telecomms_churn_clean, 
                      family = binomial(link = "logit"))

summary(model_multiple)


```


```{r}
model_sans_monthly <- glm(churn ~ 
                            total_charges + contract +
                        internet_service + phone_service + tenure + 
                        dependents + senior_citizen, 
                        data = telecomms_churn_clean, 
                        family = binomial(link = "logit"))

summary(model_sans_monthly)
```


```{r}
anova(model_sans_monthly, model_multiple)
```



