---
title: "ggplot homework"
output: html_notebook
---

```{r}
library(CodeClanData)

# Process data into arguments needed by plot()
regions <- levels(as.factor(whisky$Region))
colours0 <- seq(length(regions))
colours <- as.numeric(as.factor(whisky$Region))

# Call plot
plot(
  x = whisky$YearFound, y = whisky$Capacity, col = colours, type = "p", log = "y", pch = 16,
  xlab = "Year Founded", ylab = "Distillery Capacity"
)

# Add legend
legend(1948, 2.51e07, legend = regions, col = colours0, pch = 16)
```

```{r}
#recreate the above graph using ggplot 
library(tidyverse)

names(whisky)
ggplot(whisky) +
  aes(x = YearFound, y = Capacity) + 
  geom_point(aes(colour = Region)) + 
  scale_x_continuous() + 
  scale_y_log10()
```
2 - Faceting 
```{r}
library(janitor)
guerry <- clean_names(Guerry)

head(guerry)

```


1.Use facetting to investigate the relationship between crimes rates against property vs against persons, and how they differ between regions.

```{r}
ggplot(guerry, aes(x = crime_prop, y = crime_pers)) +
  geom_point() + 
  facet_wrap(~ region)
```

2. Also try introducing a simple linear model between crime rates (and an error ribbon) using geom_smooth() to each facet.

```{r}
ggplot(guerry, aes(x = crime_prop, y = crime_pers)) +
  geom_point() + 
  geom_smooth() + 
  facet_wrap(~ region)

```

3. Repeat the process for literacy rates (you will need to bin literacy rates into categories).

```{r}

guerry$literacy

guerry <- guerry %>% 
  mutate(literacy_grouped = cut_number(literacy, 4))

ggplot(guerry, aes(x = literacy_grouped, y = crime_pers)) +
  geom_point() + 
  geom_smooth() + 
  facet_wrap(~ region) + 
  geom_jitter()
```

3. Scales and Coordinates
```{r}
hills2000
```

1. Produce a scatter plot of speed vs climb with a linear regression model fitted to the data using geom_smooth(method = "lm).

```{r}
names(hills2000)

ggplot(hills2000, aes(x = speed, y = climb)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```



2. Use scale to apply a log10 transform to the climb.
```{r}
ggplot(hills2000, aes(x = speed, y = climb)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  scale_y_log10()
```


3. Rename the axes appropriately, and show units on the axis titles.
```{r}
ggplot(hills2000, aes(x = speed, y = climb)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  scale_y_log10() + 
  labs(
    y = "Climb (ft)", 
    x = "Speed (mph)"
  )
```
4. Relabel the x-axis to be evenly spaced.
```{r}
ggplot(hills2000, aes(x = speed, y = climb)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  scale_y_log10() + 
  labs(
    y = "Climb (ft)", 
    x = "Speed (mph)"
  ) 
```


5. Colour points and linear model based on sex.
```{r}
ggplot(hills2000, aes(x = speed, y = climb)) + 
  geom_point(aes(colour = Sex)) + 
  geom_smooth(aes(colour = Sex), method = "lm") + 
  scale_y_log10() + 
  labs(
    y = "Climb (ft)", 
    x = "Speed (mph)"
  ) 
```

6. Facet the plot by sex.
```{r}
ggplot(hills2000, aes(x = speed, y = climb)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  scale_y_log10() + 
  labs(
    y = "Climb (ft)", 
    x = "Speed (mph)"
  )  + facet_grid(~Sex)
```


7. Zoom in to the plot so only speeds between 4mph and 11mph are shown. Be careful not to alter the linear model in doing so.
```{r}
ggplot(hills2000, aes(x = speed, y = climb)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  scale_y_log10() + 
  labs(
    y = "Climb (ft)", 
    x = "Speed (mph)"
    ) + 
  coord_cartesian(xlim = c(4, 11))
```

