---
title: "R Notebook"
output: html_notebook
---


Create connection to acme_employees database 
```{r}
library(keyring)

library(RPostgreSQL)

keyring_unlock("local")

username <- key_get(service = "postgresql_username", keyring = "local")

password <- key_get(service = "postgresql_password", keyring = "local")

keyring_lock("local")


db_connection <- dbConnect(drv = PostgreSQL(), 
                              user = username,
                              password = password, 
                              dbname = "acme_employees", 
                              host = "localhost")

rm(username)
rm(password)
```


```{r}


acme_employees_df <- dbGetQuery(db_connection, 
           "SELECT * FROM employees")
```


Create a full name field 

```{r}
acme_employees_df <- dbGetQuery(db_connection,
                                "SELECT * FROM employees,
                                CONCAT(first_name, ' ', last_name) AS full_name")
```



```{r}
acme_employees_tname <- dbGetQuery(db_connection,
           "SELECT e.id, e.first_name, e.last_name, e.email, t.name AS team_name
           FROM employees AS e INNER JOIN teams AS t
           ON e.team_id = t.id")
```



```{r}
dbGetQuery(db_connection,
           "SELECT COUNT(e.id) AS num_employees, t.name AS team_name
           FROM employees AS e RIGHT JOIN teams AS t
           ON e.team_id = t.id
           GROUP BY t.name
           ORDER BY num_employees DESC
           NULLS LAST")
```


```{r}

dbGetQuery(db_connection,
          "SELECT (id), first_name, last_name, email FROM 
          employees WHERE email IS NULL
          OR  email NOT LIKE '%@%'")
```

```{r}
acme_employees_missing_name <- dbGetQuery(db_connection,
           "SELECT e.id, e.first_name, e.last_name, e.email, t.name AS team_name
           FROM employees AS e INNER JOIN teams AS t
           ON e.team_id = t.id
           WHERE e.first_name IS NULL
           OR e.first_name LIKE '_' ")
```




2 API MVP 

```{r}
library(keyring)
library(httr)
library(purrr)

```

```{r}

 
 keyring_unlock("remote")
  indico_api_key <- key_get(service = "indico_api_key", keyring = "remote")
  keyring_lock("remote")
  

get_emotions_from_indico_api <- function(message){
  
 
  params <- list(
      api_key = indico_api_key,
      data = message
  )
  
 
  url <- "https://apiv2.indico.io/emotion/"
  response <- POST(url = url, query = params)
  
  
 content(response)
  

}




```



```{r}


get_emotions_from_indico_api("I really like working here, great place, decent perks")




```

```{r}


messages_1 <- c("I really like working here, great place, decent perks", "Hmm, not so sure I'll stay: long working hours and low pay, bad morale")

map(.x = messages_1, .f = get_emotions_from_indico_api)

```



```{r}
messages <- c("What a nice place to work, I love my colleagues.", "politics and cliques, it's really difficult to fit in here, we need more teambuilding exercises", "My boss is lovely, she is genuinely interested in my development, and takes time each day for a chat", "I really want to quit as soon as possible, I feel stuck")





emotions <- map(.x = messages, .f = get_emotions_from_indico_api)
```

```{r}
library(purrr)

str(emotions)
flatten_emotions <- flatten(emotions)

flatten_emotions
```

```{r}
anger <- map_dbl(flatten_emotions, "anger")
fear <- map_dbl(flatten_emotions, "fear")
joy <-      map_dbl(flatten_emotions, "joy")
sadness <-  map_dbl(flatten_emotions, "sadness")
surprise <- map_dbl(flatten_emotions, "surprise")
emotions_df <- data.frame(
  messages = messages,
  anger = anger,
  fear = fear,
  joy = joy,
  sadness = sadness,
  surprise = surprise
  )
emotions_df
```




Extensions 

AcmeCorp would like mean values of each of the five emotions, averaging over all of the employee messages they have stored in their database. Based on the work you did above, pass all of the messages held in the feedbacks table through the emotions API endpoint, storing the output in a data frame. Next, calculate the mean value of each of the emotions stored in this data frame. [Hint - beware of NAs when calculating mean(). Sometimes the API may not return a valid response for a message (this will appear as NA values), so set na.rm = TRUE in mean()]
```{r}
# First, pass the messages held in feedbacks through the emotions api 

# Get the feedback data into R 


keyring_unlock("local")

username <- key_get(service = "postgresql_username", keyring = "local")

password <- key_get(service = "postgresql_password", keyring = "local")

keyring_lock("local")


db_connection <- dbConnect(drv = PostgreSQL(), 
                              user = username,
                              password = password, 
                              dbname = "acme_employees", 
                              host = "localhost")

rm(username)
rm(password)
acme_feedback <- dbGetQuery(db_connection, 
           "SELECT message FROM feedbacks")


acme_feedback_list <- as.list(acme_feedback)

acme_fb <- flatten(acme_feedback_list)

acme <- flatten(acme_fb)

```

Next, pass the messages from the feedback table into the API 
```{r}

acme_feedback_emotions <- map(.x = acme, .f = get_emotions_from_indico_api)


acme_feedback_emotions

acme_feedback_emotions <- flatten(acme_feedback_emotions)

acme_feedback_emotions

anger <-    map_dbl(acme_feedback_emotions, "anger")
fear <-     map_dbl(acme_feedback_emotions, "fear")
joy <-      map_dbl(acme_feedback_emotions, "joy")
sadness <-  map_dbl(acme_feedback_emotions, "sadness")
surprise <- map_dbl(acme_feedback_emotions, "surprise")
acme_emotions_df <- data.frame(
  feedback = acme_feedback,
  anger = anger,
  fear = fear,
  joy = joy,
  sadness = sadness,
  surprise = surprise
  )
acme_emotions_df
```


Calculate the mean value of each of the emotions in the dataframe
```{r}

map(.x = acme_emotions_df, .f = mean, na.rm = TRUE)


```




```{r}

try_employees <- dbGetQuery(db_connection,
           "SELECT e.first_name, e.last_name, t.id, t.name, f.message
           FROM (employees AS e INNER JOIN teams AS t 
           ON e.team_id = t.id)
           INNER JOIN feedbacks AS f
           ON e.id = f.employee_id")

try_employees_1 <- map(.x = try_employees$message, .f = get_emotions_from_indico_api)

```


```{r}

flattened_employees <- flatten(try_employees_1)

anger <-    map_dbl(flattened_employees, "anger")
fear <-     map_dbl(flattened_employees, "fear")
joy <-      map_dbl(flattened_employees, "joy")
sadness <-  map_dbl(flattened_employees, "sadness")
surprise <- map_dbl(flattened_employees, "surprise")
employees_emotions_df <- data.frame(
  first_name = try_employees$first_name, 
  last_name = try_employees$last_name, 
  team_name = try_employees$name,
  feedback = acme_feedback,
  anger = anger,
  fear = fear,
  joy = joy,
  sadness = sadness,
  surprise = surprise
  )

employees_emotions_df
```


```{r}
subset(employees_emotions_df, max(joy))

subset(emplo)

```

```{r}

max(employees_emotions_df$joy)

max(employees_emotions_df$anger)


joy <- map_dbl(employees_emotions_df$joy, max, na.rm = TRUE)
max(joy)


detach("package:RPostgreSQL", unload=TRUE)
```

```{r}
library(sqldf)

sqldf("SElECT MAX(joy), first_name, last_name, team_name, message FROM employees_emotions_df ")
```

```{r}
sqldf("SElECT MAX(anger), first_name, last_name, team_name, message FROM employees_emotions_df ")
```

